Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-10-12 paper/paper.tex
update list of keywords
rephrase paragraph 2 from intro

\begin{keyword}
\kwd{audio databases}
\kwd{continuous wavelet transform}
\kwd{demodulation}
\kwd{distance learning}
\kwd{human--computer interaction}
\kwd{music information retrieval.}
\end{keyword}

@@

Despite their widespread use, purely linguistic references to timbre fail to convey the intention of the composer.
On the one hand, adjectives such as \emph{bright} or \emph{rough} are prone to misunderstanding, as they do not prescribe any musical gesture that is capable of achieving them \cite{antoine2018isma}.
On the other hand, the sole mention of a playing technique does not specify its effect in terms of auditory perception.
For instance, although the term \emph{breathy} alludes to a playing technique that is peculiar to wind instruments, a cellist may accomplish a seemingly breathy timbre by bowing near the fingerboard, i.e., \emph{sul tasto} in the classical terminology.
Yet, such acoustical similarity at the scale of the entire instrumentarium is not directly reflected by the semantic similarity between playing technique denominations; and discovering it requires musical expertise \cite{kolozali2011ismir}.

@@

Given an audio stimulus $\boldsymbol{x}_n$ from our perceptual study, we seek its position in the cluster graph $\mathcal{G}_0$.
Then, we identify its IMT triplet, scrape for audio samples in SOL matching this triplet, and assign them all to the same cluster as the original audio stimulus.
We repeat the same procedure for all $N=78$ nodes in $\mathcal{G}_0$, resulting in $N^\prime = 9346$ samples in total.
This is a form of semi-supervised label propagation: from a limited amount of human annotation, we curate a relatively large subset of SOL, amounting to about one third of the entire dataset ($9346$ out of $25444$ samples). % \vl: ?

>>>>

\begin{keyword}
\kwd{audio databases}
\kwd{audio similarity}
\kwd{continuous wavelet transform}
\kwd{demodulation}
\kwd{distance learning}
\kwd{human--computer interaction}
\kwd{music information retrieval.}
\end{keyword}

@@

Despite their widespread use, purely linguistic references to timbre fail to convey the intention of the composer.
On the one hand, adjectives such as \emph{bright} or \emph{rough} are prone to misunderstanding, as they do not prescribe any musical gesture that is capable of achieving them \cite{antoine2018isma}.
On the other hand, the sole mention of a playing technique does not specify its effect in terms of auditory perception.
For instance, although the term \emph{breathy} alludes to a playing technique that is peculiar to wind instruments, a cellist may accomplish a seemingly breathy timbre by bowing near the fingerboard, i.e., \emph{sul tasto} in the classical terminology.
Yet, in a diverse instrumentarium, the semantic similarity between playing technique denominations does not reflect such acoustical similarity \cite{kolozali2011ismir}.

@@

Given an audio stimulus $\boldsymbol{x}_n$ from our perceptual study, we seek its position in the cluster graph $\mathcal{G}_0$.
Then, we identify its IMT triplet, scrape for audio samples in SOL matching this triplet, and assign them all to the same cluster as the original audio stimulus.
We repeat the same procedure for all $N=78$ nodes in $\mathcal{G}_0$, resulting in $N^\prime = 9346$ samples in total.
This is a form of semi-supervised label propagation: from a limited amount of human annotation, we curate a relatively large subset of SOL, amounting to about one third of the entire dataset ($9346$ out of $25444$ samples).
